Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-10 paper/sec-results.tex

@@

In the boosted case, the sum of the $2b2j$ and $4j$ components is almost as large as the
irreducible $4b$ background, thus increasing the total background rates by a factor 2 as compared
to the case where only $4b$ is accounted for.
%
This effect is more dramatic in the intermediate and resolved categories: in the former,
$2b2j$ completely dominates the background (thus the increase in $S/sqrt{B}$ noted in
Table~\ref{table:cutflow4B}  when only the $4b$ component is kept), and in the latter
it is comparable to $4b$.
%
Therefore, we conclude that an accurate estimate of the fake $b$-tag contribution is
an essential component of this analyses, and that complete QCD multijet samples
should be included.

  {\bf add plots BKG}

>>>>

In the boosted case, the sum of the $2b2j$ and $4j$ components is almost as large as the
irreducible $4b$ background, thus increasing the total background rates by a factor 2 as compared
to the case where only $4b$ is accounted for.
%
This effect is more dramatic in the intermediate and resolved categories: in the former,
$2b2j$ completely dominates the background (thus the increase in $S/\sqrt{B}$ noted in
Table~\ref{table:cutflow4B}  when only the $4b$ component is kept), and in the latter
it is comparable to $4b$.
%
Therefore, we conclude that an accurate estimate of the fake $b$-tag contribution is
an essential component of this analyses, and that complete QCD multijet samples
should be included.

In Fig.~\ref{fig:histoBack} we show the decomposition of the background for one important kinematical
distribution, the $p_T$ of the leading reconstructed Higgs candidate, various background
components, for both the boosted and the resolved categories.
%
In the same figure we also show the results of the corresponding comparison
at the level of the $p_T^{hh}$ of the
reconstructed di-Higgs system.
%
The histograms correspond to the distributions at the end of the cut-based
analysis.
%
The results are consistent with those summarized in
Table~\ref{table:cutflowBack}: in the boosted case we see how $4b$ is the most important
component of the background, with $2b2j$ being of the same order of magnitude, while
for the resolved category we see that $2b2j$ dominates instead.
%
So the effect of the fakes is certainly important, but fortunately it is not a limiting factor
in the resolved category, the one that leads to higher signal significance.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_boost_back.pdf}
  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_res_back.pdf}
  \includegraphics[width=0.49\textwidth]{plots/pt_HH_C2_boost_back.pdf}
  \includegraphics[width=0.49\textwidth]{plots/pt_HH_C2_res_back.pdf}
  \caption{\small
    Upper plots: the decomposition of the QCD multijet background in its various
    components, $4b$, $2b2j$ and $4j$, for the $p_T$ of the leading
    Higgs candidate in the boosted (left plot) and resolved (right plot) categories.
    %
    Lower plots: the same comparison this time for the $p_T^{hh}$ of the
    reconstructed di-Higgs system.
}
\label{fig:histoBack}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@
